---
title: "Project"
format: pdf
editor: visual
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = TRUE, results = "hold")
library(tidyverse)
library(ggplot2)
library(comprehenr)
library(tidymodels)
library(modelr)
default_theme <- theme(
    # Title
    plot.title = element_text(
      color = "white", size = 14,  
      face = "bold", hjust = 0.5),
    plot.subtitle = element_text(
      color = "lightgray", size=10, 
      face = "italic", hjust = 0.5),
    # Axis Text
    axis.title.x = element_text(
      color = "lightgray",  
      size = 12, angle = 0,
    ),
    axis.title.y = element_text(
      color = "lightgray",  
      size = 12, angle = 90,
    ),
    axis.text.x = element_text(
      face = "italic", color = "lightgray",  
      size = 8, angle = -15),
    axis.text.y = element_text(
      face = "italic", color = "lightgray",  
      size = 8, angle=45),
    # Background Colors
    panel.background = element_rect(
      fill = "#060606", colour = "#5f5d63",
      linewidth = 2, linetype = "solid"),
    panel.grid.major = element_line(
      linewidth = 0.5, linetype = 'solid', 
      colour = "#7a797a"), 
    panel.grid.minor = element_line(
      linewidth = 0.25, linetype = 'solid', 
      colour = "#585759"),
    plot.background = element_rect(fill = "#0e0e0f"),
    # Legend
    legend.title = element_text(color = "lightgray", size = 10),
    legend.text = element_text(color = "gray"),
    legend.key = element_rect(fill = "#383838", color = NA),
    legend.background = element_rect(fill = "#5f5d63"),
  )
```

# Introduction

```{r}
# https://www.kaggle.com/datasets/jackdaoud/esports-earnings-for-players-teams-by-game
teams <- as_tibble(read_csv('highest_earning_teams.csv', col_types="dcddcc"))

players <- as_tibble(read_csv('highest_earning_players.csv', col_types="dccccdcc"))
summary(players)
players

locations <- as_tibble(read_csv('country-and-continent-codes-list.csv', col_types="cccccd"))
summary(locations)
locations

# https://www.kaggle.com/datasets/rankirsh/esports-earnings
general <- as_tibble(read_csv('GeneralEsportData.csv',col_types='cdcdddd'))
summary(general)
general

historical <- as_tibble(read_csv('HistoricalEsportData.csv', col_types='Dcddd'))
summary(historical)
historical

# https://www.kaggle.com/datasets/rankirsh/evolution-of-top-games-on-twitch/data
twitch_games <- as_tibble(read_csv("Twitch_game_data.csv", col_types='dcccdddddddd')) %>%
  mutate(Date=date(paste(Year, Month, "01", sep="-")))
summary(twitch_games)
twitch_games
```

# Observations

## Teams

```{r}
summary(teams)
```

### TeamID

```{r}
team_ids <- sort(unique(teams$TeamId))

teams %>%
  ggplot(mapping = aes(x=TeamId)) +
  geom_histogram(binwidth=1, color='white', alpha=0.7) +
  labs(
    title="Count of Each Team ID",
    x = "Team ID",
    y = "Count"
  ) + default_theme
```

```{r}
# Proportion of teams with multiple entries
(length(team_ids) - length(unique(team_ids)))/(length(team_ids))
teams %>% # Only show the teams with multiple entries
  filter(duplicated(TeamId)) %>%
  arrange(TeamId)
```

Team IDs are in two different groups, should we redefine TeamIDs for our dataset?

Teams are listed repeatedly for each game they play

### TotalUSDPrize

```{r}
#team_ids <- sort(unique(teams$TeamId))
arrange(teams, desc(TotalUSDPrize))
teams %>%
  ggplot(mapping = aes(x=TeamId, y=TotalUSDPrize)) +
  geom_col(color='white', alpha=0.7) +
  labs(
    title="Total Tournaments of Each Team",
    x = "Team ID",
    y = "Tournament Count",
  ) + default_theme
```

### TotalTournaments

```{r}
#arrange(teams, desc(TotalTournaments)) %>%
#  group_by(TeamId)
teams %>%
  ggplot(mapping = aes(x=TeamId, y=TotalTournaments)) +
  geom_col(color='white', alpha=0.7) +
  labs(
    title="Total Tournaments of Each Team",
    x = "Team ID",
    y = "Tournament Count",
  ) + default_theme
teams %>%
  ggplot(mapping = aes(x=Game, y=TotalTournaments)) +
  geom_boxplot(color='white', alpha=0.7) +
  labs(
    title="Team Tournament Counts by Game",
    x = "Game",
    y = "Team Tournament Counts",
  ) + default_theme
```

### Games

```{r}
#game_list <- unique(teams$Game)
#game_list
teams %>%
  ggplot(mapping = aes(x=Game)) +
  geom_bar(color='white', alpha=0.7) +
  labs(
    title="Count of Teams in Each Game",
    x = "Game",
    y = "Count of Teams",
  ) + default_theme
```

This only has the top 100 teams in the top 10 grossing games. Hearthstone and Arena of Valor have less than 100 teams listed here. Why?

### Genre

```{r}
teams %>%
  ggplot(mapping = aes(x=Genre)) +
  geom_bar(color='white', alpha=0.7) +
  labs(
    title="Count of Teams in Each Genre",
    x = "Genre",
    y = "Count of Teams"
  ) + default_theme
```

## Highest Earning Players

-   TotalUSD Prize looks good
-   Country code should be useful
-   So should Game and Genre

## Locations

-   Mostly just used for mapping - revisit later

## General Esports Data

-   Total players of 0 seems weird
-   Total Tournaments of 0 also seems weird
-   Total earnings of 0 seems weird.
-   Release date 1981-2023

## Historical Data

-   

# Data Descriptions

## Highest Earning Teams

## Highest Earning Players

## Locations

-   

## General Esports Data

-   Game: Game name
-   ReleaseDate: Date of release
-   Genre: Genre of game
-   TotalEarnings: Total prizepool allocated in tournaments
-   OfflineEarnings: Amount of earnings allocated in
-   PercentOffline: Percentage of the offline community
-   TotalPlayers: Total players of both online and offline
-   TotalTournaments: Total tournaments played

## Historical Data

-   Date: The month that some set of tournaments happened for this game
-   Game: The game in question (name)
-   Earnings: Total amount earned by players in tournaments for this game.
-   Players: Number of players to whom earnings were distributed.
-   Tournaments: Number of tournaments for this game this month.

```{r}

ggplot(data=teams, mapping=aes(x=Game)) +
  geom_histogram(stat='count', binwidth=100)

merged <- merge(historical, select(general, Game, Genre))
# Put the values in a data frame and convert to millions usd

#merged <- merged %>% 
#as.Date(merged$Date,origin = "1970-01-01")

merged <- merged %>%
  mutate(date = as.Date(merged$Date,origin="1970-01-01"),
    year = format(date, "%Y"))

merged <- merged %>%
 # mutate(year=year.start(Date))
  group_by(year) %>%
  #filter(year != as.date('2023-01-01')) %>%
  filter(year != 2023) %>%
  mutate(earnings_million=Earnings/1000000) %>%
  ungroup()

earnings_data <- merged

yearly_earnings_line <- earnings_data %>%
  ggplot(mapping = aes(x=year, y=earnings_million)) +
  geom_col(mapping = aes(fill = Genre))
yearly_earnings_line <- yearly_earnings_line + labs(
  title = "Tournament Earnings over Time",
  subtitle="Total Yearly Payout to Players Across Major Tournaments",
  x = "Year", y = "Gross Earnings (Millions USD)"
) + default_theme

yearly_earnings_line <- yearly_earnings_line + theme(
  plot.title = element_text(color = "black", size = 20, 
                            face = "bold", hjust = 0.5),
  plot.subtitle = element_text(color = "black",
                               face = "italic", hjust = 0.5),
  ) + 
    default_theme + 
     theme (
      axis.text.x = element_text(angle = 45)
    )
yearly_earnings_line
```

```{r}
#merged <- merge(historical, select(general, Game, Genre))
merged <- merged %>%
#  mutate(year=year.start(Date)) %>%
  mutate(earnings_million=Earnings/1000000) %>%
 filter(year != 2023)
#merged
# Put the values in a data frame and convert to millions usd
for (genre in unique(merged$Genre)) {
  earnings_data <- merged %>%
    filter(Genre == genre)
  yearly_earnings_line <- earnings_data %>%
    ggplot(mapping = aes(x=year, y=earnings_million)) +
    geom_col()
  yearly_earnings_line <- yearly_earnings_line + labs(
    title = "Tournament Earnings over Time",
    subtitle=paste("Total Yearly Payout to ", genre, " Players"),
    x = "Year", y = "Gross Earnings (Millions USD)"
  )
  yearly_earnings_line <- yearly_earnings_line + theme(
    plot.title = element_text(color = "black", size = 20, 
                              face = "bold", hjust = 0.5),
    plot.subtitle = element_text(color = "black",
                                 face = "italic", hjust = 0.5),
    )
  print(yearly_earnings_line)
  #ggsave(paste("figs/", genre), yearly_earnings_line)
}
```

# Training and Testing

Training model for all Data

#60 training 20% testing 20% validation

```{r}
set.seed(12345)

#teams model
teams <- teams %>% mutate(
  Game = as_factor(Game),
  Genre = as_factor(Genre),
  TeamName = as_factor(TeamName))
teams_split <- initial_split(teams, prop = .6)
teams_train <- training(teams_split)
other <- testing(teams_split)

teams_split2 <- initial_split(other, prop = .5)
teams_test <- training(teams_split2)
teams_valid <- testing(teams_split2)


#players model
players <- players %>% mutate(
  NameFirst = as_factor(NameFirst),
  NameLast = as_factor(NameLast),
  CurrentHandle = as_factor(CurrentHandle),
  CountryCode = as_factor(CountryCode),
  Game = as_factor(Game),
  Genre = as_factor(Genre))

players_split <- initial_split(players, prop = .6)
players_train <- training(players_split)
other2 <- testing(players_split)

players_split2 <- initial_split(other2, prop = .5)
players_test <- training(players_split2)
players_valid <- testing(players_split2)


#locations model
locations <- locations %>% mutate(
  Continent_Name = as_factor(Continent_Name),
  Continent_Code = as_factor(Continent_Code),
  Two_Letter_Country_Code = as_factor(Two_Letter_Country_Code),
  Three_Letter_Country_Code = as_factor(Three_Letter_Country_Code),
  Country_Name = as_factor(Country_Name))

locations_split <- initial_split(locations, prop = .6)
locations_train <- training(locations_split)
other3 <- testing(locations_split)

locations_split2 <- initial_split(other3, prop = .5)
locations_test <- training(locations_split2)
locations_valid <- testing(locations_split2)


#general model
general <- general %>% mutate(
  Game = as_factor(Game),
  Genre = as_factor(Genre))

general_split <- initial_split(general, prop = .6)
general_train <- training(general_split)
other4 <- testing(general_split)

general_split2 <- initial_split(other4, prop = .5)
general_test <- training(general_split2)
general_valid <- testing(general_split2)


#historical model
historical$Date <- as.numeric(difftime(historical$Date, min(historical$Date), units = "days"))

historical <- historical %>% mutate(
  Game = as_factor(Game))

historical_split <- initial_split(historical, prop = .6)
historical_train <- training(historical_split)
other5 <- testing(historical_split)

historical_split2 <- initial_split(other5, prop = .5)
historical_test <- training(historical_split2)
historical_valid <- testing(historical_split2)

#twitch_games model
twitch_games$Date <- as.numeric(difftime(twitch_games$Date, min(twitch_games$Date), units = "days"))
twitch_games$Month <- as.numeric(as.character(twitch_games$Month))
twitch_games$Year <- as.numeric(as.character(twitch_games$Year))
twitch_games <- twitch_games %>% mutate(
  Game = as_factor(Game))

twitch_games_split <- initial_split(twitch_games, prop = .6)
twitch_games_train <- training(twitch_games_split)
other6 <- testing(twitch_games_split)

twitch_games_split2 <- initial_split(other6, prop = .5)
twitch_games_test <- training(twitch_games_split2)
twitch_games_valid <- testing(twitch_games_split2)

```

Correlations between numeric attributes(converted ones as well)

```{r}
#teams
t_train <- cor(teams_train %>% select(TeamId, TotalUSDPrize, TotalTournaments))
print(t_train)

#players
p_train <- cor(players_train %>% select(PlayerId, TotalUSDPrize))
print(p_train)

#general
g_train <- cor(general_train %>% select(ReleaseDate, TotalEarnings, TotalPlayers, TotalTournaments, OfflineEarnings, PercentOffline))
print(g_train)

#historical
h_train <- cor(historical_train %>% select(Date, Earnings, Players, Tournaments))
print(h_train)

#twitch
tw_train <- cor(twitch_games_train %>% select(Rank, Month, Year, Hours_watched, Hours_streamed, Peak_viewers, Peak_channels, Streamers, Avg_viewers, Avg_channels, Avg_viewer_ratio, Date))
print(tw_train)
```

Validating

```{r}
#teams
teams_lmodel <- linear_reg() %>% set_engine("lm") %>% 
  fit(TotalUSDPrize ~ TotalTournaments + TeamId + Game + Genre, data = teams_train)
#Removed TeamName due to overleveling

teams_validate <- teams_valid %>% 
  bind_cols(predict(teams_lmodel, new_data = teams_valid))

print(teams_validate)

ggplot(data = teams_validate, mapping = aes(x = TotalUSDPrize, y = .pred)) + 
  geom_point() +
  geom_abline(intercept = 0, slope = 1, color = "red")

rsq <- yardstick::rsq(teams_validate, truth = TotalUSDPrize, estimate = .pred)
rmse <- yardstick::rmse(teams_validate, truth = TotalUSDPrize, estimate = .pred)
mae <- yardstick::mae(teams_validate, truth = TotalUSDPrize, estimate = .pred)

rsq
rmse
mae

results <- workflow() %>%
  add_model(linear_reg()) %>%
  add_formula(TotalUSDPrize ~ TotalTournaments + TeamId + Game + Genre) %>%
  fit_resamples(vfold_cv(teams_train, v=5),
                metric_set(rsq, rmse, mae)) 

collect_metrics(results)

```

```{r}
#player
player_lmodel <- linear_reg() %>% set_engine("lm") %>% 
  fit(TotalUSDPrize ~ PlayerId  + Game + Genre, data = players_train)
#removed NameFirst, NameLast, CurrentHandle, CountryCode due to overleveling

player_validate <- players_valid %>% 
  bind_cols(predict(player_lmodel, new_data = players_valid))

print(player_validate)

ggplot(data = player_validate, mapping = aes(x = TotalUSDPrize, y = .pred)) + 
  geom_point() +
  geom_abline(intercept = 0, slope = 1, color = "red")

rsq2 <- yardstick::rsq(player_validate, truth = TotalUSDPrize, estimate = .pred)
rmse2 <- yardstick::rmse(player_validate, truth = TotalUSDPrize, estimate = .pred)
mae2 <- yardstick::mae(player_validate, truth = TotalUSDPrize, estimate = .pred)

rsq2
rmse2
mae2

results2 <- workflow() %>%
  add_model(linear_reg()) %>%
  add_formula(TotalUSDPrize ~ PlayerId  + Game + Genre) %>%
  fit_resamples(vfold_cv(players_train, v=5),
                metric_set(rsq2, rmse2, mae2)) 

collect_metrics(results2)
```

```{r}
#location
location_lmodel <- linear_reg() %>% set_engine("lm") %>% 
  fit(Country_Number ~ Continent_Code, data = locations_train)
# Continent_Name, Country_Name, Two_Letter_Country_Code, Three_Letter_Country_Code were removed due to overleveling

location_validate <- locations_valid %>% 
  bind_cols(predict(location_lmodel, new_data = locations_valid))

print(location_validate)

ggplot(data = location_validate, mapping = aes(x = Country_Number, y = .pred)) + 
  geom_point() +
  geom_abline(intercept = 0, slope = 1, color = "red")

rsq3 <- yardstick::rsq(location_validate, truth = Country_Number, estimate = .pred)
rmse3 <- yardstick::rmse(location_validate, truth = Country_Number, estimate = .pred)
mae3 <- yardstick::mae(location_validate, truth = Country_Number, estimate = .pred)

rsq3
rmse3
mae3

results3 <- workflow() %>%
  add_model(linear_reg()) %>%
  add_formula(Country_Number ~ Continent_Code) %>%
  fit_resamples(vfold_cv(locations_train, v=5),
                metric_set(rsq3, rmse3, mae3)) 

collect_metrics(results3)
```

```{r}
#general
general_lmodel <- linear_reg() %>% set_engine("lm") %>% 
  fit(TotalEarnings  ~  ReleaseDate + Genre + OfflineEarnings + PercentOffline + TotalPlayers + TotalTournaments, data = general_train)
#Removed Game due to overleveling

general_validate <- general_valid %>% 
  bind_cols(predict(general_lmodel, new_data = general_valid))

print(general_validate)

ggplot(data = general_validate, mapping = aes(x = TotalEarnings, y = .pred)) + 
  geom_point() +
  geom_abline(intercept = 0, slope = 1, color = "red")

rsq4 <- yardstick::rsq(general_validate, truth = TotalEarnings, estimate = .pred)
rmse4 <- yardstick::rmse(general_validate, truth = TotalEarnings, estimate = .pred)
mae4 <- yardstick::mae(general_validate, truth = TotalEarnings, estimate = .pred)

rsq4
rmse4
mae4

results4 <- workflow() %>%
  add_model(linear_reg()) %>%
  add_formula(TotalEarnings  ~  ReleaseDate + Genre + OfflineEarnings + PercentOffline + TotalPlayers + TotalTournaments) %>%
  fit_resamples(vfold_cv(general_train, v=5),
                metric_set(rsq4, rmse4, mae4)) 

collect_metrics(results4)
```

```{r}
#historical
historical_lmodel <- linear_reg() %>% set_engine("lm") %>% 
  fit(Earnings  ~  Date + Players + Tournaments, data = historical_train)
#Removed Game due to overleveling

historical_validate <- historical_valid %>% 
  bind_cols(predict(historical_lmodel, new_data = historical_valid))

print(historical_validate)

ggplot(data = historical_validate, mapping = aes(x = Earnings, y = .pred)) + 
  geom_point() +
  geom_abline(intercept = 0, slope = 1, color = "red")

rsq5 <- yardstick::rsq(historical_validate, truth = Earnings, estimate = .pred)
rmse5 <- yardstick::rmse(historical_validate, truth = Earnings, estimate = .pred)
mae5 <- yardstick::mae(historical_validate, truth = Earnings, estimate = .pred)

rsq5
rmse5
mae5

results5 <- workflow() %>%
  add_model(linear_reg()) %>%
  add_formula(Earnings  ~  Date + Players + Tournaments) %>%
  fit_resamples(vfold_cv(historical_train, v=5),
                metric_set(rsq5, rmse5, mae5)) 

collect_metrics(results5)
```

```{r}
#twitch
twitch_game_lmodel <- linear_reg() %>% set_engine("lm") %>% 
  fit(Peak_viewers  ~  Rank + Month + Year + Hours_watched + Hours_streamed + Peak_channels + Streamers + Avg_viewers + Avg_channels + Avg_viewer_ratio + Date, data = twitch_games_train)
#Removed Game due to overleveling

twitch_game_validate <- twitch_games_valid %>% 
  bind_cols(predict(twitch_game_lmodel, new_data = twitch_games_valid))

print(twitch_game_validate)

ggplot(data = twitch_game_validate, mapping = aes(x = Peak_viewers, y = .pred)) + 
  geom_point() +
  geom_abline(intercept = 0, slope = 1, color = "red")

rsq6 <- yardstick::rsq(twitch_game_validate, truth = Peak_viewers, estimate = .pred)
rmse6 <- yardstick::rmse(twitch_game_validate, truth = Peak_viewers, estimate = .pred)
mae6 <- yardstick::mae(twitch_game_validate, truth = Peak_viewers, estimate = .pred)

rsq6
rmse6
mae6

results6 <- workflow() %>%
  add_model(linear_reg()) %>%
  add_formula(Peak_viewers  ~  Rank + Month + Year + Hours_watched + Hours_streamed + Peak_channels + Streamers + Avg_viewers + Avg_channels + Avg_viewer_ratio + Date) %>%
  fit_resamples(vfold_cv(twitch_games_train, v=5),
                metric_set(rsq6, rmse6, mae6)) 

collect_metrics(results6)
```

Testing

```{r}
#teams
teams_testing <- teams_test %>% 
  bind_cols(predict(teams_lmodel, new_data = teams_test))

print(teams_testing)

ggplot(data = teams_testing, mapping = aes(x = TotalUSDPrize, y = .pred)) + 
  geom_point() +
  geom_abline(intercept = 0, slope = 1, color = "red")

rsq_test <- yardstick::rsq(teams_testing, truth = TotalUSDPrize, estimate = .pred)
rmse_test <- yardstick::rmse(teams_testing, truth = TotalUSDPrize, estimate = .pred)
mae_test <- yardstick::mae(teams_testing, truth = TotalUSDPrize, estimate = .pred)

rsq_test
rmse_test
mae_test

results_test <- workflow() %>%
  add_model(linear_reg()) %>%
  add_formula(TotalUSDPrize ~ TotalTournaments + TeamId + Game + Genre) %>%
  fit_resamples(vfold_cv(teams_train, v=5),
                metric_set(rsq_test, rmse_test, mae_test)) 

collect_metrics(results_test)
```

```{r}
player_testing <- players_test %>% 
  bind_cols(predict(player_lmodel, new_data = players_test))

print(player_testing)

ggplot(data = player_testing, mapping = aes(x = TotalUSDPrize, y = .pred)) + 
  geom_point() +
  geom_abline(intercept = 0, slope = 1, color = "red")

rsq_test2 <- yardstick::rsq(player_testing, truth = TotalUSDPrize, estimate = .pred)
rmse_test2 <- yardstick::rmse(player_testing, truth = TotalUSDPrize, estimate = .pred)
mae_test2 <- yardstick::mae(player_testing, truth = TotalUSDPrize, estimate = .pred)

rsq_test2
rmse_test2
mae_test2

results_test2 <- workflow() %>%
  add_model(linear_reg()) %>%
  add_formula(TotalUSDPrize ~ PlayerId  + Game + Genre) %>%
  fit_resamples(vfold_cv(players_train, v=5),
                metric_set(rsq_test2, rmse_test2, mae_test2)) 

collect_metrics(results_test2)
```

```{r}
location_testing <- locations_test %>% 
  bind_cols(predict(location_lmodel, new_data = locations_test))

print(location_testing)

ggplot(data = location_testing, mapping = aes(x = Country_Number, y = .pred)) + 
  geom_point() +
  geom_abline(intercept = 0, slope = 1, color = "red")

rsq_test3 <- yardstick::rsq(location_testing, truth = Country_Number, estimate = .pred)
rmse_test3 <- yardstick::rmse(location_testing, truth = Country_Number, estimate = .pred)
mae_test3 <- yardstick::mae(location_testing, truth = Country_Number, estimate = .pred)

rsq_test3
rmse_test3
mae_test3

results_test3 <- workflow() %>%
  add_model(linear_reg()) %>%
  add_formula(Country_Number ~ Continent_Code) %>%
  fit_resamples(vfold_cv(locations_train, v=5),
                metric_set(rsq_test3, rmse_test3, mae_test3)) 

collect_metrics(results_test3)
```

```{r}
general_testing <- general_test %>% 
  bind_cols(predict(general_lmodel, new_data = general_test))

print(general_testing)

ggplot(data = general_testing, mapping = aes(x = TotalEarnings, y = .pred)) + 
  geom_point() +
  geom_abline(intercept = 0, slope = 1, color = "red")

rsq_test4 <- yardstick::rsq(general_testing, truth = TotalEarnings, estimate = .pred)
rmse_test4 <- yardstick::rmse(general_testing, truth = TotalEarnings, estimate = .pred)
mae_test4 <- yardstick::mae(general_testing, truth = TotalEarnings, estimate = .pred)

rsq_test4
rmse_test4
mae_test4

results_test4 <- workflow() %>%
  add_model(linear_reg()) %>%
  add_formula(TotalEarnings  ~  ReleaseDate + Genre + OfflineEarnings + PercentOffline + TotalPlayers + TotalTournaments) %>%
  fit_resamples(vfold_cv(general_train, v=5),
                metric_set(rsq_test4, rmse_test4, mae_test4)) 

collect_metrics(results_test4)
```

```{r}
historical_testing <- historical_test %>% 
  bind_cols(predict(historical_lmodel, new_data = historical_test))

print(historical_testing)

ggplot(data = historical_testing, mapping = aes(x = Earnings, y = .pred)) + 
  geom_point() +
  geom_abline(intercept = 0, slope = 1, color = "red")

rsq_test5 <- yardstick::rsq(historical_testing, truth = Earnings, estimate = .pred)
rmse_test5 <- yardstick::rmse(historical_testing, truth = Earnings, estimate = .pred)
mae_test5 <- yardstick::mae(historical_testing, truth = Earnings, estimate = .pred)

rsq_test5
rmse_test5
mae_test5

results_test5 <- workflow() %>%
  add_model(linear_reg()) %>%
  add_formula(Earnings  ~  Date + Players + Tournaments) %>%
  fit_resamples(vfold_cv(historical_train, v=5),
                metric_set(rsq_test5, rmse_test5, mae_test5)) 

collect_metrics(results_test5)
```

```{r}
twitch_game_testing <- twitch_games_test %>% 
  bind_cols(predict(twitch_game_lmodel, new_data = twitch_games_test))

print(twitch_game_testing)

ggplot(data = twitch_game_testing, mapping = aes(x = Peak_viewers, y = .pred)) + 
  geom_point() +
  geom_abline(intercept = 0, slope = 1, color = "red")

rsq_test6 <- yardstick::rsq(twitch_game_testing, truth = Peak_viewers, estimate = .pred)
rmse_test6 <- yardstick::rmse(twitch_game_testing, truth = Peak_viewers, estimate = .pred)
mae_test6 <- yardstick::mae(twitch_game_testing, truth = Peak_viewers, estimate = .pred)

rsq_test6
rmse_test6
mae_test6

results_test6 <- workflow() %>%
  add_model(linear_reg()) %>%
  add_formula(Peak_viewers  ~  Rank + Month + Year + Hours_watched + Hours_streamed + Peak_channels + Streamers + Avg_viewers + Avg_channels + Avg_viewer_ratio + Date) %>%
  fit_resamples(vfold_cv(twitch_games_train, v=5),
                metric_set(rsq_test6, rmse_test6, mae_test6)) 

collect_metrics(results_test6)
```

# Sources

https://www.esportsearnings.com
